\documentclass{homework}
\usepackage{graphicx}
\usepackage{amsmath}
\title{MAE 3195, Credit Sheet 1}
\author{DUE Jan. 22, 2014}
\begin{document}
For this tutorial homework, work through Lesson 1 in your text ProEngineer Tutorial. You will need files provided by the textbook publisher on the CD-ROM that accompanies your textbook. Insert the CD-ROM that accompanies your textbook. Close the software that automatically launches (hitting Esc at Macromedia screen might work).

\begin{enumerate}
\item Pro/E by double clicking on the Wildfire icon on the desktop.
\item Set the working directory to appropriate directory on CD-ROM. Select File>Working Directory from the drop down menu. Then browse to select PROEWILDFIRE/Supplemental Files/Educational.
\item You are now prepared for the activities in Lesson 1.
\end{enumerate} 

Since this is a tutorial homework, each individual must perform this work independently. You are encouraged, however, to discuss the assignment with other students as necessary. You are permitted to use your textbook and Pro/E on-line help as necessary.

It is recommended that you study the “Questions for Review” and create some of the “Exercise” models at the end of the chapter. After completing the lesson, answer the following questions and bring this Credit Sheet with you to class on the due date.
\problem{} List and summarize how the mouse buttons can be used to pan, spin, and zoom the graphics.
%\solution

\problem{} Explain why datum planes have two colors.
%\solution

\problem{} What is meant by the term "preselection"?
%\solution
    
\problem{} What is meant by the term "regeneration"?
%\solution

\problem{} What is the regeneration sequence? How can you determine it for a part?
%\solution

\end{document}


