\documentclass{homework}
\usepackage{graphicx}
\usepackage{amsmath}
\title{Notes Lecture 1.2}
\author{Jon Torrey}

\begin{document}

\textbf{Class overview and design practices}

\begin{enumerate}
  \item Review syllabus, expectations, timeline
  \item Review breif latex outline and how homeworks will be assigned and collected
  \item What is CAx? ProE v Catia v Unigraphics
  \item Why is it needed? Concurrent engineering to reduce cost
  \item What is good design? Apple MBP. Reduces human error. Presents a plesent user interface. Reduces cost without the expense of quality.
  \item What is design intent? A logical hierarchy of design that minimizes excess features, links parent-child relationships correct, references datums-faces-edges-points
  \item "Effective design and manufacturing, both necessary to produce high quality products, are closely related. However, effective design is a prerequiste for effective manufacturing; quality cannot be manufactured or tested into a product, it must be design in."
\end{enumerate}

\textbf{Welcome to ProE}

\begin{enumerate}
  \item Set working directory
  \item New part
  \item Part properties, units, material, etc
  \item Walk through of mouse buttons
  \item Walk through of interface ribbons
  \item Walk through of parametric and feature based modeling and the hierarchy
  \item Model hierarchy, sketch to feature, when to keep sketch seperate
  \item Sketcher, geometric primatives extruded into 3D, contraints, dimensioning, strong v weak
  \item Revolves, axis of revolution, construction lines
  \item Bolt example, proper dimensioning
  \item Drawing files
  \item Dynamically changing dimensions of parts, regeneration
\end{enumerate}

\end{document}
