\documentclass[12pt]{article}

% Packages
\usepackage{lastpage} 
\usepackage{fancyhdr}	%For header and footer
\usepackage{amsmath, amsthm, amssymb} %For mathematics
\usepackage{graphicx}
\usepackage{hyperref}	%For hyperlinks

% Page setup
\setlength{\topmargin}{-0.4in}
\setlength{\topskip}{0.3in}    % between header and text
\setlength{\textheight}{9.in} % height of main text
\setlength{\textwidth}{6.5in}    % width of text
\setlength{\oddsidemargin}{0in} % odd page left margin
\setlength{\evensidemargin}{0in} % even page left margin
\setlength{\parindent}{0pt}	% Suppress the indent

% Macros
\newcommand*{\bv}[1]{\textbf{#1}} % Write vectors in bold case within an equation environment

% Header and Footer
\pagestyle{fancy}%\fancyhead{}
\fancyhf{}	% Clear the default header and footer
\fancyhead[L]{MAE 3195 \\ Name:}
\fancyhead[R]{Credit Sheet 2 \\ \thepage /\pageref{LastPage}}


% Title
\title{MAE 3195, Credit Sheet 2, Tutorial Lesson 2\\
Creating a Simple Object (Part I)}
\date{}

% Body of document
\begin{document}
\maketitle

For this homework, read and work through Lesson 2 in your text \textit{ProEngineer Tutorial}. During this lesson, you will create a part with a single extruded protrusion. Before you launch Pro/E, make a new sub-directory in your personal directory titled ``HW2''. Be sure to set your working directory to HW2 immediately after launching Pro/E. When you create this part, your text suggests that you name it ``block'', but instead, you MUST name it ``***-hw2'' where the three asterisks indicate your initials.\\

Since this is a tutorial homework, each individual must perform this work independently. You are encouraged, however, to discuss the assignment with other students as necessary.\\

It is recommended that you study the “Questions for Review” and create some of the ``Exercise'' models at the end of the chapter. After completing the lesson, answer the following questions and bring this Credit Sheet with you to class on the due date.

\pagebreak

\section*{Review Questions}
\begin{enumerate}
	\item What is the purpose of the sketching reference?
	\vspace{1.25in}
	\item Summarize the implicit rules of sketcher.
	\vspace{1.25in}
	\item Where are your Pro/E files stored when they are saved?
	\vspace{1.25in}
	\item What is meant by a``blind protrusion''?
	\vspace{1.25in}
	\item When you look at a sketch, in which direction will a solid protrusion occur?
\end{enumerate}

\end{document}